MultifidelityTrajectoryOptimization

### 2024-12-12 artefacts/paper.tex
plot convergence distance from optimum for mlmc

Where the number of columns after which the next one is selected is determined by the ratio $r_{hl} = n_{u_l} / n_{u_h}$.
This gives us $u_{hlr} = T_{hlr} u_h$, which can be compared with $u_l$.

To downsample $u_h$ to $u_l$ by averaging, we need the ratio $r_{lh} = n_{u_h} \ n_{u_l}$.
We can then multiply $u_h$ with a matrix $T_{hla}$ of size $n_{u_l} \times n_{u_h}$:

>>>>

Where the number of columns after which the next one is selected is determined by the ratio $r_{hl} = n_{u_h} / n_{u_l}$.
This gives us $u_{hlr} = T_{hlr} u_h$, which can be compared with $u_l$.

To downsample $u_h$ to $u_l$ by averaging, we need the ratio $r_{lh} = n_{u_h} / n_{u_l}$.
We can then multiply $u_h$ with a matrix $T_{hla}$ of size $n_{u_l} \times n_{u_h}$:
